Forecasting the 2024 U.S. Presidential Election: A Poll-Based Approach

### 2024-11-03 paper/paper.qmd
Update state_votes correspondence.

intercept_wide$`Votes` <- c(6, 11, 10, 15, 19, 16, 16)

>>>>

# Used dictionary-like vector to ensure the correct correspondence
state_votes <- c(
  Nevada = 6,
  Arizona = 11,
  Wisconsin = 10,
  Michigan = 15,
  Pennsylvania = 19,
  `North Carolina` = 16,
  Georgia = 16
)

# Use the named vector to add the votes to intercept_wide
intercept_wide <- intercept_wide %>%
  mutate(Votes = state_votes[State])
